Lens Modeling in \sw

### 2013-09-09 text/tex/results.tex
test setup

\section{Results} \label{sec:results}

>>>>

\section{The lens modeling challenge} \label{sec:results}

\subsection{\sw} \label{sec:SpaceWarps}
some words about \sw

\subsection{The simulated lenses} \label{sec:sims}

In order to estimate users performance, \sw included some simulated lensing configurations in their image set.

There are three kinds of simulated lenses.

Sims produced using {\tt gravlens}
\citep{2001astro.ph..2341K,2001astro.ph..2340K}.

\begin{itemize}
  \item {\em Quasar:\/} A singular elliptical isothermal plus constant
    external shear, with a circular Gaussian source.
  \item {\em Galaxy:\/} Lens as with quasar, but elliptical de
    Vaucouleurs source.
  \item {\em Galaxy:\/} Lens is circular NFW plus one dominant
    elliptical SIE and perturbating elliptical SIEs, source as with
    galaxy.
\end{itemize}

Singular isothermal is in equations (33-35) of
\cite{2001astro.ph..2341K} with core radius set to zero. NFW is
equations (48,50) of the same paper, and shear is the $\gamma$ term in
equation (76) of that work.

\subsection{The test setup} \label{sec:testsetup}

We made use of the simulated lenses (sims) to test the volunteers abilities to model those sims.

The testing was done with a small number of volunteers ($N_\text{v}=4$) and a set of simulated configurations ($N_\text{sim}=29$) chosen to represent some typical configurations.
The volunteers were given an introduction video explaining the theory behind gravitational lensing and the usage of \spl.
Additionally the volunteers had the opportunity to pose general questions to the experts during several hangouts during the training phase that preceded the modeling challenge.\footnote{No questions about the to be modeled sims were answered.}

To estimate the performance of the volunteers and the quality of the generated models, two test T1 and T2 were done.
%\begin{enumerate}
%  \item (T1) Correct identification of extremal points
%  \item (T2) Reproduction of the mass distribution of the lens
%\end{enumerate}

T1 tested the volunteers ability to reconstruct the arrival time surface given a survey image containing a sim.
This task consists of two parts.
First, the correct identification and location of lensed images (T1a).
Second to find the correct ordering in respect of the arrival time for the identified lensed images (T1b).

While we expected T1a to be trivial, given the nature of the survey images and the success of \sw, we expect T1b to pose more problems.
T1b tests the volunteers understandings of the theory of arrival time surfaces and the odd number theorem.
While we can provide the volunteers with some general rule of thumbs, T1b involves a lot of imagination and guessing and therefore a training effect could be visible in this test.

T1 was also designed to give some feedback on the difficulties volunteers encounter, to further imrove the tutorial materials.

The second test T2 was to compare the desired results of a modeling process, the mass distribution of the lens $\kappa(x, y)$.
To get a means of comparing the simulated data (sims) to the generated modeled data (models), the total convergence, also called enclosed mass $\kappa_{\text{encl}}(r)$ for both was calculated.
The Einstein radius $\Theta_E$ is defined by $\kappa_{\text{encl}}(\Theta_E)=1$ and gives a number that allows the comparison between the sims and the models.

\todo{!} Should I write down prior expectation for T2 too?
